Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-26 ms.qmd
Re-work some text on mean-variance relationships

#### *Mean-variance relationships justify use of $lnCVR_{Q_{10}}$*
We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats. We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean in physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses. We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.

@@

Overall, we found that the relationship between the mean and SD of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the relative variance in physiological rates does not increase proportionally as the mean increases. Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`).

>>>>

#### *Mean-variance relationships justify use of $lnCVR_{Q_{10}}$*
We explored mean-variance relationships for the acute and acclimation responses across all traits and habitats. We estimated the scaling relationship between log standard deviation in physiological rates [log(SD)] and log mean physiological rates [log(mean)], accounting for non-independence resulting from effects coming from the same species, study and traits (i.e., random effects of species, study and trait) as done in our main analyses. We also included an interaction between log(mean) and habitat type to better understand how the scaling relationship between log(SD) and log(mean) varies across habitats.

@@

Overall, we found that the relationship between log(mean) and log(SD) of the acute and acclimation responses was generally linear, suggesting that the use of $lnCVR_{Q_{10}}$ was justified (@fig-mv). Overall, the scaling relationship between log(SD) and log(mean) was sub-linear across all habitats (Freshwater = $\Beta$ = `r fixef(model_mv1)[2]`, 95% CI: `r fixef(model_mv1)[2,3]` to  `r fixef(model_mv1)[2,4]`; Marine = $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[5,4]`; Terrestrial: $\Beta$ = `r fixef(model_mv1)[2] + fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[2,3] + fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[2,4] + fixef(model_mv1)[6,4]`) suggesting that the variance in physiological rates does not increase proportionally as the mean increases. Importantly, the scaling relationship between log(SD) and log(mean) differed significantly between habitats (Freshwater compared to Marine: Contrast = `r fixef(model_mv1)[5]`, 95% CI: `r fixef(model_mv1)[5,3]` to `r fixef(model_mv1)[5,4]` and Terrestrial to Marine: Contrast = `r fixef(model_mv1)[6]`, 95% CI: `r fixef(model_mv1)[6,3]` to `r fixef(model_mv1)[6,4]`), which helps explain the relative .
